Declarative Integration of Interactive 3D Graphics into the World-Wide Web:\\Principles, Current Approaches, and Research Agenda \\~

### 2013-03-07 Web3D2013-Dec3D/paper.tex
new images

\begin{figure*}%[ht]
  \centering
  \includegraphics[width=\linewidth]{images/x3dom_apps.png}
  \caption{Some X3DOM applications. From left to right: walktrough of Roman heritage site; cultural heritage object explorer with metadata; web-based design review application with annotation markers; rendering big data sets, here the Boeing 777, in the Web browser using an ``out-of-browser'' approach. (The Boeing 777 commercial airplane model is courtesy of Boeing. License granted by David Kasik, Boeing.)}
  \vspace{-0.2cm}
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=1.0\textwidth]{images/ch_apps.png}
  \caption{From left to right: walktrough of Roman heritage site; cultural heritage object explorer with metadata; restored virtual synagoge.}
  \vspace{-0.2cm}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=1.0\textwidth]{images/cad_apps.png}
  \caption{From left to right: web-based design review application with annotation markers; interactive explosion of CAD model on iPad; lightweight web-based viewer for 3D CAD data; visualization and interactive exploration of simulation data by using extended mouse events.}
  \vspace{-0.2cm}
\end{figure*}
